\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2013-12-16 paper/paper.tex
add link to github
Cite todoFRP, forum properly

Just how novel is this small, but hugely significant change? The
\href{http://docs.elm-lang.org/library/Graphics/Input.elm\#hoverables}{documentation}
for \texttt{hoverables} states that it allows users to ``create and
destroy elements dynamically and still detect hover information,'' but
gives no further indicators on how to do so. Though the Elm website is
full of examples, there are none for either \texttt{hoverable} or
\texttt{hoverables}. Moreover, in the
\href{https://groups.google.com/d/msg/elm-discuss/QgowLy5jdhA/CZQfjkbjMsEJ}{mailing
list post} that introduced these functions, Czaplicki said that
``\texttt{hoverables} is very low level, but the idea is that you can
build any kind of nicer abstraction on top of it.'' We have done just
that.

@@

We examine \href{https://github.com/evancz/TodoFRP}{TodoFRP}, a simple
Elm web app created by Czapliki, to provide another example of the problem
solved by \texttt{hoverableJoin}. TodoFRP is the current state-of-the-art in highly
reactive Elm GUIs. It provides examples of different levels of
reactivity, a familiar context for Elm veterans, and a few dirty tricks
of its own.

@@

@@

%Make sure to put a link to our GitHub
\bibliographystyle{alpha}
\bibliography{refs.bib}
\end{document}

>>>>

Just how novel is this small, but hugely significant change? The
\href{http://docs.elm-lang.org/library/Graphics/Input.elm\#hoverables}{documentation}
for \texttt{hoverables} states that it allows users to ``create and destroy
elements dynamically and still detect hover information,'' but gives no further
indicators on how to do so. Though the Elm website is full of examples, there
are none for either \texttt{hoverable} or \texttt{hoverables}. Moreover, in the
mailing list post that introduced these functions, Czaplicki said that
``\texttt{hoverables} is very low level, but the idea is that you can build any
kind of nicer abstraction on top of it.'' \cite{hover-forum} We have done just
that.

@@

We examine TodoFRP, \cite{todoFRP} a simple
Elm web app created by Czaplicki, to provide another example of the problem
solved by \texttt{hoverableJoin}. TodoFRP is the current state-of-the-art in highly
reactive Elm GUIs. It provides examples of different levels of
reactivity, a familiar context for Elm veterans, and a few dirty tricks
of its own.

@@

Our code is available at \url{https://github.com/ealter/Elm-GUIs}.

@@

\bibliographystyle{alpha}
\bibliography{refs.bib}
\end{document}
